%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Classicthesis-Styled CV
% LaTeX Template
% Version 1.0 (22/2/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Alessandro Plasmati
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%https://www.dropbox.com/sh/lsou2626lus11kd/AAAYAWzZ57jvnRpbtvBvknZ0a
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{scrartcl}

\reversemarginpar % Move the margin to the left of the page 

\newcommand{\MarginText}[1]{\marginpar{\raggedleft\itshape\small#1}} % New command defining the margin text style

\usepackage[nochapters]{classicthesis} % Use the classicthesis style for the style of the document
\usepackage[LabelsAligned]{currvita} % Use the currvita style for the layout of the document
\usepackage{graphicx}
\usepackage[export]{adjustbox}
\usepackage{wrapfig}
\usepackage{hyperref}

\renewcommand{\cvheadingfont}{\LARGE\color{Blue}} % Font color of your name at the top

\usepackage{hyperref} % Required for adding links	and customizing them
\hypersetup{colorlinks, breaklinks, urlcolor=Blue, linkcolor=Blue} % Set link colors

\newlength{\datebox}\settowidth{\datebox}{Spring 2011} % Set the width of the date box in each block

\newcommand{\NewEntry}[3]{\noindent\hangindent=2em\hangafter=0 \parbox{\datebox}{\small \textit{#1}}\hspace{1.5em} #2 #3 % Define a command for each new block - change spacing and font sizes here: #1 is the left margin, #2 is the italic date field and #3 is the position/employer/location field
\vspace{0.5em}} % Add some white space after each new entry

\newcommand{\Description}[1]{\hangindent=2em\hangafter=0\noindent\raggedright\footnotesize{#1}\par\normalsize\vspace{1em}} % Define a command for descriptions of each entry - change spacing and font sizes here

%----------------------------------------------------------------------------------------

\begin{document}

\thispagestyle{empty} % Stop the page count at the bottom of the first page

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\begin{cv}{\spacedallcaps{Jeroen Nyckees}}\vspace{1.5em} % Your name

\noindent\spacedlowsmallcaps{Personal Information}\vspace{0.5em} % Personal information heading

\NewEntry{}{\textit{Born in Brugge, Belgium,}}{4 September 1991} % Birthplace and date

\NewEntry{email}{\href{mailto:jeroen.nyckees@gmail.com}{jeroen.nyckees@gmail.com}} % Email address

\NewEntry{website}{\href{http://jenyckee.github.io}{http://jenyckee.github.io}} % Personal website

\NewEntry{phone}{(M) 0032 496 43 18 77} % Phone number(s)

\NewEntry{address}{Kardinaal lavigeriestraat 20, 1040 Etterbeek} % Phone number(s)

\NewEntry{github}{\url{http://github.com/jenyckee}}


%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS
%----------------------------------------------------------------------------------------

\noindent\spacedlowsmallcaps{Skills}\vspace{1em}

\Description{
\begin{itemize}
\item[] Application development using C++ (OpenFrameworks) and JavaScript
\item[] Sql an NoSql databases
\item[] Building cloud services using Amazon AWS
\item[] Web development and data vizualization using d3.js, React, Elm, Processing
\item[] Computer graphics: shader programming in WebGL (glsl)
\item[] Machine learning using TensorFlow (Python) and R
\item[] Very eager to learn and motivated to work on socially relevant software
\end{itemize}
}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\noindent\spacedlowsmallcaps{Work Experience}\vspace{1em}

%------------------------------------------------


\NewEntry{2017 - current}{Software engineer, \textsc{Cronos}  --- Brussels}

\Description{\MarginText{Cronos}
\begin{itemize}
\item[] Web technology consultant at public education institution of the Flemish government. I help in the development and maintenance of internal tools.
\end{itemize}}

\NewEntry{2016 - 2017}{Software engineer, \textsc{Komma Board}  --- Antwerp}

\Description{\MarginText{Komma Board}
\begin{itemize}
\item[] As a consultant at D-Studio (Mechelen) I helped developing a web application allowing architects to estimate and visualize in 3D (WebGL) real estate projects.
\item[] As a consultant at Rombit I helped developing a native application for a niche speaker manufacturer from Belgium that allows their users to control and play back music from within the app. Technologies involved were React Native and Web Sockets.
\end{itemize}}

\NewEntry{2015 - 2016}{Software engineer, \textsc{November five}  --- Antwerp}

\Description{\MarginText{November five}
\begin{itemize}
\item[] Development of web applications and animation heavy campaign websites for international clients such as New York Times.
\end{itemize}}

\NewEntry{2010 - 2014}{Teacher, \textsc{Educadomo}  --- Brussel}

\Description{\MarginText{Math teacher}
Teaching math to children from 12 to 18. Helping with planning etc.}

\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Education}\vspace{1em}

\NewEntry{2009-2012}{Vrije Universiteit Brussel, Brussel}

\Description{\MarginText{Bachelor of Computer Science}
\newline \textit{Profile : Software engineering}}

%------------------------------------------------

\NewEntry{2012-2017}{Vrije Universiteit Brussel, Brussel}

\Description{
  \MarginText{Master of Computer Science}
  \newline \textit{Profile : Web and Information Systems\\
  Thesis subject: Distributed Multi-Touch User Interfaces for Modular Musical Expression}
  \newline
  \newline
  In the context of my master thesis I developed a framework that leverages the web browser to facilitate the creation, distribution and synchronization of processing sketches to music.
  \newline
  \newline
  \textit{Covered Subjects}
  \begin{itemize}
  \item[] Parallel Programming (Erlang, Clojure, Java)
  \item[] Declarative Programming (Prolog), Functional Programming (Haskell)
  \item[] Object-Oriented Programming (SmallTalk)
  \item[] Functional Reactive Programming (Flapjax, RxJs, FrTime)
  \item[] Artificial Intelligence (R, Python)
  \item[] Data Vizualization (D3, WebGL, Java, C\#, JavaScript, C++)
  \end{itemize}
}



%------------------------------------------------

\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	Projects
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Projects}\vspace{1em}

Vizualization Belgian Federal Elections
\newline

\Description{
For a university course group project we made a data visualization for the data collected in a national poll (De stemtest) by the Flemish Radio and Television broadcasting organization and the university of Antwerp. People were asked wheter they agree or disagree on political questions. This was then compared to the positions of the different political parties in Belgium. After contacting the university of Antwerp I was able to obtain the anonymized data. The visualization gave us insights on how the level of agreement to a certain party compared to the actual post election results.
\newline\href{https://young-lake-76803.herokuapp.com/}{Stemtest visualization}
}

Vizualization Brussels Villo Bikes
\newline

\Description{
For this project I collected data from the Brussels open data platform and made a visualization that shows over time how the bike stations are being used. 
\newline\href{https://jenyckee.github.io/posts/villoviz/}{Villo visualization}
}


%------------------------------------------------

\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	OTHER INFORMATION
%----------------------------------------------------------------------------------------
\spacedlowsmallcaps{Other Information}\vspace{1em}


\vspace{1em}

\newlength{\langbox} % Create a new length for the length of languages to keep them equally spaced
\settowidth{\langbox}{English} % Length equals the length of "English" - if you have a longer language in your list put it here

\Description{\MarginText{Languages}\parbox{\langbox}{\textsc{Dutch}}\ \ $\cdotp$\ \ \ Mothertongue}

\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{\parbox{\langbox}{\textsc{English}}\ \ $\cdotp$\ \ \ Fluent}

\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{\parbox{\langbox}{\textsc{French}}\ \ $\cdotp$\ \ \ Basic (conversationally fluent)}


\vspace{1em} % Negative vertical space to counteract the vertical space between every \Description command

%------------------------------------------------

% \Description{\MarginText{Interests} Music \ \ $\cdotp$\ \ Cycling }

%----------------------------------------------------------------------------------------

\end{cv}

\end{document}